% !TEX root = ./IF-2017.tex

\newpage
\addcontentsline{toc}{section}{\hspace{-0.5cm}Document 2}
\section{CV of the Experienced Researcher}
\label{sec:cv}

The CV is intrinsic to the evaluation of the whole proposal and is
assessed throughout the three evaluation criteria by the expert
evaluators. Ensure that the information provided in Parts A and B
is fully consistent. Always mention full dates (dd/mm/yyyy) in
your CV.

\medskip\noindent
The CV should be limited to a maximum of 5 pages and should
include \textbf{the standard academic and research record}. Any
research career gaps and/or unconventional paths should be clearly
explained so that this can be fairly assessed by the independent
evaluators.

\medskip\noindent
At a minimum, the CV should contain:

\begin{enumerate}
  \item the \textbf{name} of the researcher
  \item \textbf{professional experience} (in chronological order,
  using \textbf{exact} dates)
  \item \textbf{education} (in chronological order, using
  \textbf{exact} dates)
\end{enumerate}

\medskip\noindent
The CV should also include information on:
\begin{enumerate}
  \item \textbf{Publications} in peer-reviewed conference
  proceedings and/or monographs of their respective research
  fields, indicating also the number of citations (excluding
  self-citations) they have attracted.

  \item Granted \textbf{patent(s)}.

  \item \textbf{Research monographs, chapters} in collective
  volumes and any translations thereof.

  \item \textbf{Invited presentations} to peer-reviewed,
  internationally established conferences and/or international
  advanced schools.

  \item \textbf{Research expeditions} led by the experienced
  researcher.

  \item \textbf{Organisation of International conferences} in the
  field of the researcher, including membership in the steering
  and/or programme committee.

  \item Examples of \textbf{participation in industrial innovation}.

  \item \textbf{Prizes and Awards}.

  \item \textbf{Funding} received so far.

  \item \textbf{Supervising} and \textbf{mentoring} activities.
\end{enumerate}

\textbf{In addition, researchers without a doctorate} at the call
deadline should clearly detail any period of full-time equivalent
research experience in the CV (Part B, section 4). It is essential
that the CV clearly explains how the research experience is
calculated, following the template below.\footnote{More entries
can be added if needed. This table is beyond the 5-page limit.}

\begin{table}[h!]
{\fontsize{9bp}{1em}\selectfont % should be 9pt
\newcommand{\cg}{\cellcolor{gray!20}}
\newcolumntype{M}[1]{>{\centering\arraybackslash}m{#1}}
\noindent\begin{tabular}
  {|M{.2\textwidth}|M{.2\textwidth}|M{.2\textwidth}|M{.2\textwidth}|}
\hline
\multicolumn{4}{|c|}{\cellcolor{gray!50}
  \textbf{Academic Qualifications counting towards the Total Full
  time postgraduate research experience}
}
\\ \hline
\multirow{3}{.2\textwidth}{University Degree giving access to PhD:}
  & Institution name and country
  & Date of award (a) 
  & \cellcolor{gray!90}
\\ \cline{2-3}
  & \cg{} Uni
  & \cg{} date
  & \cellcolor{gray!90}
\\ \cline{2-3}
  & \cg{} Uni
  & \cg{} date
  & \cellcolor{gray!90}
\\ \hline
\multirow{6}{.2\textwidth}{Other university degree(s)/master(s),
  if any, obtained after the award of the university degree giving
  access to PhD:} % no of rows = # masters degrees * 3
  & Institution name and country 
  & From
  & To
  % to add new, copy from here ...
\\ \cline{2-4}
  & \cg{} uni
  & \cg{} from
  & \cg{} to
\\ 
  & \multirow{2}{2cm}{Full time research experience}
  & Proportion of research activities as a percentage of the
  duration of the Master
  & Duration of research activities expressed in months
\\ 
  & & \cg{} xx\%
  & \cg{} (b)\footnote{Please count only time spent in months on
  research activities.} = xx\% * duration of Master
  % to here ...
\\ \cline{2-4}
  & \cg{} uni
  & \cg{} from
  & \cg{} to
\\ 
  & \multirow{2}{2cm}{Full time research experience}
  & Proportion of research activities as a percentage of the
  duration of the Master
  & Duration of research activities expressed in months
\\ 
  & & \cg{} xx\%
  & \cg{} (b)\footnote{Please count only time spent in months on
  research activities.} = xx\% * duration of Master
\\ \hline
\multirow{3}{.2\textwidth}{Doctorate:}
  & Institution name and country 
  & From
  & To (Date Expected)
\\ \cline{2-4}
  & \cg{} uni
  & \cg{} from
  & \cg{} to
\\ 
  & \multirow{2}{2cm}{Full time research experience}
  & \multirow{2}{2cm}{\cellcolor{gray!90}}
  & Duration of research activities expressed in months 
\\ 
  & & \cellcolor{gray!90}
  & \cg{} (c)
\\ \hline
\multicolumn{4}{|c|}{\cellcolor{gray!50}
  \textbf{Other research activities counting towards the total
  full-time postgraduate research experience}
} \\
\multirow{3}{.2\textwidth}{Institution:}
  & Institution name and country 
  & From
  & To (Date Expected)
\\ \cline{2-4}
  & \cg{} uni
  & \cg{} from
  & \cg{} to
\\ 
  & \multirow{2}{2cm}{Full time research experience}
  & \multirow{2}{2cm}{\cellcolor{gray!90}}
  & Duration of research activities expressed in months 
\\ 
  & & \cellcolor{gray!90}
  & \cg{} (d)
\\ \hline
\multicolumn{3}{|c|}{\cellcolor{gray!50}
  \textbf{Total full-time postgraduate research experience: number
  of months}
}
  & \cellcolor{gray!50} =(b)+(c)+(d)
\\ \hline
\end{tabular}}
\end{table}

\newpage

\section{Capacity of the Participating Organisations}
\label{sec:capacities}

\ul{List of participating organisations (one page)}

\medskip\noindent
Please provide a list of all participating organisations (both
beneficiaries and, where applicable, the entity with a capital or
legal link to the beneficiary and the partner
organisation\footnote{All partner organisations should be listed
here, including secondments}) indicating the legal name, the
department carrying out the work and the supervisor.

\medskip\noindent
If a secondment in Europe is planned but the partner organisation
is not yet known, as a minimum the type of organisation foreseen
(academic/non-academic) must be stated.

\medskip\noindent
Any inter-relationship between different participating
organisation(s) or individuals and other entities/persons (e.g.
family ties, shared premises or facilities, joint ownership,
financial interest, overlapping staff or directors, etc.)
\textbf{must} be declared and justified \textbf{in this part of
the proposal}.

\newcommand\rotx[1]{\rotatebox[origin=c]{90}{\textbf{#1}}}
\newcommand\roty[1]{\rotatebox[origin=c]{90}{\parbox{4cm}{\raggedright\textbf{#1}}}}
\newcommand\MyHead[2]{\multicolumn{1}{l|}{\parbox{#1}{\centering #2}}}

\noindent\begin{tabular}{|m{2.5cm}|m{1cm}|c|c|m{3cm}|}
\hline
  \textbf{Participants}
& \MyHead{1cm}{\textbf{Legal\\Entity\\Short\\Name}}
& \textbf{Country}
& \textbf{Supervisor}
& \MyHead{2.5cm}{\textbf{Role of\\Partner\\Organisation\footnotemark}} \\
\hline
\ul{Beneficiary} & & & & \cellcolor{gray!90}\\\hline
- NAME  & & & & \cellcolor{gray!90} \\\hline
Entity with a capital or legal link & & & & \cellcolor{gray!90}\\\hline
- NAME  & & & & \cellcolor{gray!90}\\\hline
\ul{Partner} \ul{\mbox{Organisation}} & & & & \\\hline
- NAME  & & & & \\\hline
\end{tabular}
\vspace{\baselineskip}
\footnotetext{For example hosting secondments, for GF hosting the outgoing phase, etc.}

\medskip\noindent


\noindent Complete the following table. 1 page for each
role---choose one of:
\begin{itemize}
  \item beneficiary (compulsory)
  \item entity with a capital or legal link to the beneficiary (optional)
  \item partner organisation for GD (compulsory for GF only)
  \item partner organisation for secondment (optional)

\end{itemize}
\begin{table}[h!]
{\fontsize{9bp}{1em}\selectfont % should be 9pt
\noindent\begin{tabular}{|>{\raggedright}p{.25\textwidth}|p{.7\textwidth}|}\hline
  \multicolumn{2}{|c|}{\cellcolor{gray!50}
    \textbf{[Full name + Legal Entity Short Name + Country]}
  } \\\hline
\textbf{General Description} &

\\\hline
\textbf{Academic organisation} &
  Yes / No

\\\hline
\textbf{Role and profile of key persons (supervisor)} &
{\em (names, title, qualifications of the main supervisor)}
{\em }
\\\hline
\textbf{Dept./Division/Laboratory} &

\\\hline
\textbf{Key research facilities, Infrastructure and Equipment} &
{\em
Demonstrate that the beneficiary has sufficient facilities and
infrastructure to host and/or offer a suitable environment for
training and transfer of knowledge to the recruited experienced
researcher If applicable, indicate the name of the entity with a
capital or legal link to the beneficiary and its role in the
action in the following table.
}
\\\hline
\textbf{Independent research premises?} &
{\em Please explain the status of the beneficiary's research
facilities\----i.e. are they owned by the beneficiary or rented by
it? Are its research premises wholly independent from other
entities? If applicable, indicate the name of the entity with a
capital or legal link to the beneficiary and describe the nature
of the link..} 
\\\hline
\textbf{Previous and current involvment in research} &
{\em Indicate up to 5 \textbf{relevant} EU national or
international research and training actions/projects in which the
beneficiary has previously participated} \\\hline
\textbf{Current involvement in Research and Training Programmes} &
\\\hline
\textbf{Relevant publications and/or research/innovation products} &
{\em (Max 5) Only list items (co-)produced by the supervisor}
\\\hline
\end{tabular}}
\end{table}

\section{Ethical Issues}
\label{sec:ethics}

Compliance with the relevant ethics provisions is essential from
the beginning to the end of the action and is an integral part of
research funded by the European Union within Horizon 2020. 

\medskip\noindent
Applicants submitting research proposals for funding within Marie
Sk\'{l}odowska-Curie actions in Horizon 2020 should demonstrate
proactively that they are aware of and will comply with European
and national legislation and fundamental ethical principles,
including those reflected in the
\href{http://www.europarl.europa.eu/charter/pdf/text_en.pdf}{Charter
of Fundamental Rights of the European Union} and the
\href{http://www.echr.coe.int/Documents/Convention_ENG.pdf}{European
Convention on Human Rights and its Supplementary Protocols}.

\medskip\noindent 
Please be aware that it is the applicants' responsibility to
identify any potential ethical issue, to handle the ethical
aspects of the proposal and to detail how these aspects will be
addressed.

\bigskip\noindent
{\large {\bf \ul{The Ethics Review Procedure in Horizon 2020}}}

\medskip\noindent
All proposals above threshold and considered for funding will
undergo an Ethics Review carried out by independent ethics
experts.  When submitted a proposal to Horizon 2020, all
applicants are required to complete an Ethics Issues Table (EIT in
the Part A of the proposal.  Applicants who flag ethical issues in
the EIT have to also complete a more in-depth Ethics
Self-Assessment in Part B.

\medskip\noindent

The ethics self-assessment will become part of the Grant Agreement
and may thus lead to binding obligations. The Grant Agreement can
only be signed if all ethics requirement have been duly addressed.
The ethics review result will distinguish between ethics
requirements to be addressed before Grant Agreement signature and
those that can be cleared at a later stage (e.g. ethics approvals
to be submitted before the start of the action task). In the
latter case, a separate work package ‘Ethics Requirements’ listing
the deliverables will be created automatically.

\medskip\noindent

For more details, please refer to the H2020
\href{http://ec.europa.eu/research/participants/data/ref/h2020/grants_manual/hi/ethics/h2020_hi_ethics-self-assess_en.pdf}{``How
to complete your Ethics Self-Assessment'' guide}.

\bigskip\noindent

{\large {\bf \ul{Ethics Self-Assessment (Part B)}}}

\medskip\noindent
The Ethics Self-Assessment must:

{\bf
\begin{enumerate}
  \item Describe how the proposal meets the EU and national legal and ethics requirements of the country/countries where the task raising ethical is to be carried out.
\end{enumerate}
}

\medskip\noindent
For more information on how to deal with Third Countries\footnote{In the
context of ethics appraisal, Third Country refers to non-EU
country; Associated Countries are "ethics" TC} please see Article
34 of the
\href{http://ec.europa.eu/research/participants/data/ref/h2020/grants_manual/amga/h2020-amga_en.pdf}{Annotated
Model Grant Agreement}, as well as the following
\href{https://ec.europa.eu/info/law/law-topic/data-protection_en}{rules
for the protection of personal data inside and outside the EU}.
Please ensure and confirm that the research performed outside the
EU is compatible with the Union, National and International
legislation and could have been legally conducted in one of the EU
Member States. 

\medskip\noindent

Please list the documents provided with their expiry date.

\medskip\noindent
Ensure early compliance of the proposed research with EU and
national legislation on ethics in research.  Should your proposal
be selected for funding, you will be required - if applicable - to
confirm that you have obtained the following documents needed for
implementing the action tasks in question:
\begin{itemize}
  \item 
    any ethics committee opinion required under national law and 
  \item
    any notification or authorisation for activities raising
    ethical issues required under national and/or European law 
\end{itemize}

\medskip\noindent

If you have not already applied for/received the ethics
approval/required ethics documents when submitting the proposal,
please indicate in this section the approximate date when you will
obtain the missing approval/any other ethics documents. Please
state explicitly that you will not proceed with any research with
ethical implications before obtaining the necessary
authorizations/opinions.

\medskip\noindent
\fcolorbox{black}{gray!50}{\parbox{.95\textwidth}{
  \emph{The documents must be kept on file and be submitted upon
  request by the beneficiary to the REA (see Article 52). If
  they are not in English, they must be submitted together with an
  English summary, which shows that the action tasks in question
  are covered and includes the conclusions of the committee or
  authority concerned (if available).}

  \medskip\noindent
  \emph{If you plan to request these ethics documents specifically
  for your proposed action, your request must contain an explicit
  reference to the action's title.}
}}

\bigskip

{\bf
\begin{enumerate}[resume, start=2]
  \item Explain in detail how you intend to address the ethical
  issues flagged, in particular with regard to:
\end{enumerate}
} \begin{itemize}
    \item the research \textbf{objectives} (e.g., study
    of vulnerable populations, cooperation with a Third Country,
    etc.);

    \item t the research {\bf methodology} (e.g., clinical trials,
    involvement of children and related information and
    consent/assent procedures, data protection and
    privacy issues related to data collected, etc.);

    \item the potential {\bf impact} of the research (e.g. dual
    use issues, environmental damage, malevolent use, etc.).

    \item appropriate health and safety procedures --- conforming to
    relevant local/national guidelines/legislation --- for the staff
    involved 
    
    \item possible harm to the environment the research might
    cause (e.g. environmental risks of nanomaterials), and
    measures that will be taken to mitigate the risks.
\end{itemize}

In order to facilitate the ethics review of the proposal, please
confirm (delete as appropriate):

[\dots TO DO: ethics table from template \dots]

\section{Letters of commitment (GF only)}
\label{sec:letters}

For the Global Fellowship proposals, a letter of commitment
\textbf{of the partner organisations} (hosting the outgoing phase
in a third country) must be included in Part B-2 to ensure their
real and active participation.  Do not attach this letter as a
separate PDF file or as an embedded file since this makes them
invisible in the proposal. GF Proposals which fail to include a
\emph{letter of commitment} of the partner organisation will be
declared \textbf{inadmissible}.

\medskip\noindent

Minimum requirements for the letter of commitment:
\begin{itemize}
  \item heading or stamp from the institution; 
  \item up-to-date (may not be dated prior to the call
  publication);
  \item the text must demonstrate the will to actively participate
  in the (identified) proposed action and the precise role.
\end{itemize}

\medskip\noindent

Please note that no template for these letters is provided, only
general rules.
